О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-09 pps-linear-bound/pps-linear-lower-bound.tex
Improve some citations

The most significant breakthrough on the planar case was done by Solymosi~\cite{solymosi2003note},
who proved that $cn \leq d(2,n)$ for a sufficiently small constant $c$.
Following the details of Solymosi's proof carefully,
one can know out that the inequality holds at least for $c = 1/24$.
The constant was improved in~\cite{our-mz-rus,our-vmmsh-2018}
to $1/8$ for all $n$ and $3/8$ for sufficiently big $n$, respectively.

>>>>

The most significant breakthrough on the planar case was done by Solymosi~\cite{solymosi2003note},
who proved that $cn \leq d(2,n)$ for a sufficiently small constant $c$.
Following the details of Solymosi's proof carefully,
one can know out that the inequality holds at least for $c = 1/24$.
(See~\cite[Exercise 2.6]{garibaldi2005erdos} for some remarks.)
The constant was improved in~\cite{our-mz-rus}to $1/8$ for all $n$ and in~\cite{our-vmmsh-2018}
to $3/8$ for sufficiently big $n$.
